### 2022-02-18 paper/output/document/AMA_possible.tex
started chapter 4

%
\begin{isabellebody}%
\setisabellecontext{AMA{\isacharunderscore}possible}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Is Automated Kantian Ethics Possible?%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Many philosophers are averse to the idea that a computer could perform ethical 
reasoning or that the categorical imperative could provide an algorithm for
moral judgement. For example, Rawls asserts, ``it is a serious misconception to think of the CI-procedure 
as an algorithm intended to yield, more or less mechanically, a correct judgment. There is no such 
algorithm, and Kant knows this" \citep[166]{rawlslectures}. Ebels-Duggan also claims, ``no one supposes that the Categorical
Imperative provides a mechanical algorithm that delivers all by itself a complete account of what we 
ought to do in any given situation" \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
may seem, these claims are not obvious and require further justification. Philosophers who believe 
that mental activity completely determines moral reasoning,\footnote{what's the name for these
guys? do they have a name?} must explain why computers can, in theory, simulate certain mental processes like arithmetic 
and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
it is not obvious that it is theoretically impossible to automate ethical reasoning. After all, computers may eventually 
learn to simulate human mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.

@@

%:%150=122%:%
%:%151=123%:%

@@

%:%158=129%:%
%:%159=130%:%

@@

>>>>

%
\begin{isabellebody}%
\setisabellecontext{AMA{\isacharunderscore}possible}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Is Automated Kantian Ethics Possible?%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
SAY THAT ALSO APPLIES TO VIRTUE ETHICS AND THAT MIMICING IS GOOD

Many philosophers are averse to the idea that a computer could perform ethical
reasoning or that the categorical imperative could provide an algorithm for
moral judgement. For example, Rawls asserts, ``it is a serious misconception to think of the CI-procedure 
as an algorithm intended to yield, more or less mechanically, a correct judgment. There is no such 
algorithm, and Kant knows this" \citep[166]{rawlslectures}. Ebels-Duggan also claims, ``no one supposes that the Categorical
Imperative provides a mechanical algorithm that delivers all by itself a complete account of what we 
ought to do in any given situation" \citep[174]{ebelsduggan}. However unmechanical ethical reasoning
may seem, these claims are not obvious and require further justification. Philosophers who believe 
that mental activity completely determines moral reasoning,\footnote{what's the name for these
guys? do they have a name?} must explain why computers can, in theory, simulate certain mental processes like arithmetic 
and language, but cannot perform ethical reasoning. Without a soul or God-based account of ethical reasoning, 
it is not obvious that it is theoretically impossible to automate ethical reasoning. After all, computers may eventually 
learn to simulate human mental activity entirely, as shown by progress in brain simulation \citep{brainsimulation}.

@@

%:%148=120%:%
%:%149=121%:%

@@

%:%156=128%:%
%:%157=129%:%

@@

%:%173=144%:%
%:%174=145%:%

### 2022-02-18 paper/output/document/appendix.tex
started chapter 4

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Appendix%
}
\isamarkuptrue%
%
\isamarkupsubsection{Maxims and Motives \label{maximmotive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim \cite{whatisamaxim}. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

%:%97=62%:%
%:%109=64%:%
%:%110=65%:%
%:%111=66%:%

@@

%:%122=70%:%
%:%134=72%:%
%:%135=73%:%
%:%136=74%:%

@@

%:%139=76%:%
%:%140=76%:%
%:%143=78%:%
%:%144=79%:%
%:%145=80%:%

@@

@@

%:%150=84%:%
%:%152=85%:%
%:%153=85%:%
%:%155=86%:%
%:%156=87%:%
%:%159=89%:%
%:%160=90%:%
%:%161=91%:%

@@

@@

%:%166=95%:%
%:%167=96%:%
%:%168=97%:%
%:%169=97%:%
%:%170=98%:%
%:%171=99%:%
%:%172=99%:%
%:%173=100%:%
%:%174=101%:%
%:%175=101%:%
%:%176=102%:%

@@

%:%180=106%:%

@@

%:%183=108%:%
%:%184=109%:%
%:%185=110%:%
%:%186=110%:%
%:%187=111%:%
%:%188=114%:%

@@

%:%192=118%:%
%:%193=119%:%

@@

%:%198=123%:%
%:%201=125%:%
%:%202=126%:%
%:%203=127%:%

@@

@@

%:%209=132%:%
%:%210=133%:%
%:%211=134%:%

@@

%:%213=135%:%
%:%215=135%:%
%:%219=135%:%
%:%220=135%:%
%:%222=136%:%
%:%223=137%:%
%:%224=138%:%

@@

%:%235=141%:%
%:%236=142%:%
%:%237=143%:%

@@

@@

%:%247=152%:%
%:%248=153%:%
%:%249=154%:%

@@

%:%251=155%:%
%:%253=155%:%
%:%257=155%:%
%:%258=155%:%
%:%260=156%:%
%:%261=157%:%
%:%262=158%:%

@@

%:%273=162%:%
%:%274=163%:%
%:%275=164%:%

@@

%:%283=173%:%

@@

%:%285=174%:%
%:%286=175%:%

@@

%:%288=176%:%
%:%290=176%:%
%:%294=176%:%
%:%295=176%:%
%:%297=177%:%
%:%298=178%:%
%:%299=179%:%

@@

%:%310=182%:%
%:%311=183%:%
%:%312=184%:%

@@

%:%316=187%:%
%:%319=189%:%
%:%320=190%:%
%:%321=191%:%

@@

@@

%:%326=195%:%
%:%327=196%:%
%:%328=197%:%

@@

%:%330=198%:%
%:%332=198%:%
%:%336=198%:%
%:%337=198%:%
%:%339=199%:%
%:%340=200%:%
%:%341=201%:%

@@

%:%352=204%:%
%:%353=205%:%
%:%362=210%:%
%:%374=212%:%
%:%375=213%:%
%:%376=214%:%

@@

%:%380=217%:%
%:%381=217%:%
%:%382=218%:%
%:%384=219%:%
%:%385=220%:%
%:%386=221%:%
%:%389=223%:%
%:%391=225%:%
%:%392=225%:%
%:%393=226%:%
%:%394=227%:%
%:%395=227%:%
%:%397=227%:%
%:%401=227%:%
%:%402=227%:%
%:%404=228%:%
%:%405=229%:%
%:%406=230%:%

@@

%:%419=235%:%
%:%421=237%:%
%:%422=237%:%
%:%424=239%:%
%:%426=241%:%
%:%427=241%:%
%:%428=241%:%
%:%430=241%:%
%:%434=241%:%
%:%435=241%:%
%:%437=242%:%
%:%438=243%:%
%:%439=244%:%

@@

%:%450=247%:%
%:%451=248%:%
%:%452=249%:%

@@

%:%462=253%:%
%:%474=255%:%
%:%475=256%:%
%:%476=257%:%

@@

%:%486=265%:%
%:%490=267%:%
%:%491=268%:%
%:%492=269%:%

@@

%:%495=271%:%
%:%497=272%:%
%:%498=273%:%
%:%499=274%:%

@@

%:%504=278%:%
%:%505=279%:%
%:%506=280%:%
%:%507=280%:%
%:%508=281%:%
%:%511=282%:%
%:%515=282%:%
%:%516=282%:%
%:%518=283%:%
%:%519=284%:%
%:%529=286%:%
%:%530=287%:%
%:%531=288%:%

@@

%:%550=305%:%
%:%551=306%:%

@@

%:%554=308%:%
%:%556=309%:%
%:%557=309%:%
%:%558=310%:%
%:%559=311%:%
%:%560=311%:%
%:%561=312%:%
%:%564=313%:%
%:%568=313%:%
%:%569=313%:%
%:%570=314%:%
%:%571=314%:%
%:%572=315%:%
%:%573=315%:%
%:%574=316%:%
%:%575=316%:%
%:%576=316%:%
%:%577=317%:%
%:%587=319%:%
%:%588=320%:%
%:%589=321%:%

@@

%:%594=324%:%
%:%598=326%:%
%:%599=327%:%
%:%600=328%:%
%:%604=330%:%
%:%605=331%:%

@@

%:%608=333%:%
%:%621=354%:%
%:%622=355%:%
%:%623=355%:%
%:%625=356%:%
%:%626=357%:%
%:%627=358%:%

@@

%:%631=361%:%
%:%633=362%:%
%:%634=363%:%
%:%635=363%:%
%:%636=364%:%
%:%637=365%:%
%:%638=365%:%
%:%640=366%:%
%:%641=367%:%
%:%644=369%:%
%:%645=370%:%

@@

%:%648=372%:%
%:%649=373%:%
%:%650=374%:%
%:%651=374%:%
%:%653=374%:%
%:%657=374%:%
%:%658=374%:%
%:%660=375%:%
%:%661=376%:%
%:%662=377%:%

@@

%:%676=383%:%
%:%677=384%:%
%:%678=385%:%
%:%681=387%:%
%:%682=388%:%
%:%683=389%:%

@@

%:%689=394%:%
%:%691=396%:%
%:%692=396%:%
%:%693=397%:%
%:%696=398%:%
%:%700=398%:%
%:%701=398%:%
%:%703=399%:%
%:%709=399%:%
%:%712=400%:%
%:%713=401%:%
%:%714=401%:%
%:%715=402%:%
%:%716=403%:%

@@

%:%718=404%:%
%:%720=404%:%
%:%724=404%:%
%:%725=404%:%
%:%727=405%:%
%:%728=406%:%
%:%729=407%:%

@@

%:%741=411%:%
%:%742=412%:%
%:%743=413%:%

@@

%:%753=422%:%
%:%754=423%:%
%:%755=424%:%

@@

%:%773=435%:%
%:%785=437%:%
%:%786=438%:%
%:%787=439%:%

@@

%:%790=441%:%
%:%791=442%:%
%:%792=443%:%

@@

%:%794=444%:%
%:%796=444%:%
%:%800=444%:%
%:%801=444%:%
%:%803=445%:%
%:%804=446%:%
%:%805=447%:%

@@

%:%816=450%:%
%:%817=451%:%
%:%818=452%:%
%:%822=454%:%
%:%824=456%:%
%:%825=456%:%
%:%826=457%:%
%:%827=458%:%

@@

%:%829=459%:%
%:%831=459%:%
%:%835=459%:%
%:%836=459%:%
%:%838=460%:%
%:%839=461%:%
%:%840=462%:%

@@

%:%851=465%:%
%:%852=466%:%

@@

%:%855=468%:%
%:%856=469%:%
%:%857=470%:%

@@

%:%859=471%:%
%:%861=471%:%
%:%865=471%:%
%:%866=471%:%
%:%868=472%:%
%:%869=473%:%
%:%870=474%:%

@@

%:%882=478%:%
%:%883=479%:%

@@

%:%886=481%:%
%:%887=482%:%
%:%888=483%:%
%:%891=484%:%
%:%895=484%:%
%:%896=484%:%
%:%897=484%:%
%:%906=486%:%
%:%907=487%:%
%:%908=488%:%

@@

@@

%:%912=491%:%
%:%913=492%:%
%:%914=493%:%
%:%917=494%:%
%:%921=494%:%
%:%922=494%:%
%:%923=494%:%
%:%932=496%:%
%:%933=497%:%

@@

%:%936=499%:%
%:%937=500%:%
%:%938=501%:%

@@

%:%940=502%:%
%:%942=502%:%
%:%946=502%:%
%:%947=502%:%
%:%949=503%:%
%:%950=504%:%
%:%951=505%:%

@@

%:%962=508%:%
%:%963=509%:%
%:%964=510%:%

@@

@@

%:%970=515%:%
%:%971=516%:%
%:%972=517%:%

@@

%:%975=519%:%
%:%977=519%:%
%:%981=519%:%
%:%982=519%:%
%:%984=520%:%
%:%985=521%:%
%:%986=522%:%

@@

%:%999=527%:%
%:%1000=528%:%
%:%1001=529%:%

@@

@@

%:%1007=534%:%
%:%1008=535%:%
%:%1009=536%:%
%:%1012=537%:%
%:%1016=537%:%
%:%1017=537%:%
%:%1019=538%:%
%:%1029=540%:%
%:%1030=541%:%
%:%1032=542%:%
%:%1033=542%:%
%:%1034=543%:%
%:%1035=544%:%
%:%1036=544%:%
%:%1038=544%:%
%:%1042=544%:%
%:%1043=544%:%
%:%1045=545%:%
%:%1046=546%:%
%:%1047=547%:%

@@

%:%1072=555%:%
%:%1073=556%:%
%:%1074=557%:%

@@

%:%1084=560%:%
%:%1096=562%:%
%:%1097=563%:%
%:%1098=564%:%

@@

%:%1103=567%:%
%:%1104=568%:%

@@

%:%1107=570%:%
%:%1108=571%:%
%:%1109=572%:%
%:%1110=572%:%
%:%1111=573%:%
%:%1114=574%:%
%:%1118=574%:%
%:%1119=574%:%
%:%1120=574%:%
%:%1122=575%:%
%:%1123=576%:%
%:%1133=578%:%
%:%1134=579%:%
%:%1135=580%:%

@@

@@

%:%1150=594%:%
%:%1151=595%:%
%:%1152=596%:%

@@

%:%1154=597%:%
%:%1156=597%:%
%:%1160=597%:%
%:%1161=597%:%
%:%1163=598%:%
%:%1164=599%:%
%:%1165=600%:%

@@

%:%1178=605%:%
%:%1179=606%:%
%:%1180=607%:%

@@

%:%1185=610%:%
%:%1186=611%:%
%:%1187=612%:%

@@

%:%1190=614%:%
%:%1191=615%:%
%:%1192=615%:%
%:%1194=616%:%
%:%1195=617%:%
%:%1196=617%:%
%:%1197=618%:%
%:%1198=619%:%
%:%1199=619%:%
%:%1200=620%:%
%:%1203=621%:%
%:%1207=621%:%
%:%1208=621%:%
%:%1210=622%:%
%:%1211=623%:%
%:%1212=624%:%
%:%1222=626%:%
%:%1223=627%:%
%:%1224=628%:%

@@

@@

%:%1228=631%:%
%:%1229=632%:%
%:%1231=632%:%
%:%1235=632%:%
%:%1236=632%:%
%:%1238=633%:%
%:%1246=633%:%
%:%1247=634%:%
%:%1248=635%:%
%:%1249=635%:%
%:%1250=636%:%
%:%1252=636%:%
%:%1256=636%:%
%:%1257=636%:%
%:%1259=637%:%
%:%1269=639%:%
%:%1270=640%:%
%:%1271=641%:%
%:%1279=643%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Appendix%
}
\isamarkuptrue%
%
\isamarkupsubsection{Maxims and Motives \label{maximmotive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Add something about how I don't like KG's view because it's weaker, action will end up including
circumstances, it would have made my life easier but you can't apply it

Kitcher begins with O'Niell's circumstance, act, goal view and expands it to include the motive 
behind performing the maxim \cite{whatisamaxim}. This additional component is read 
as ``In circumstance C, I will do A in order to G because of M," where M may be ``duty" or ``self-love."
Kitcher argues that the inclusion of motive is necessary for the fullest, most general form of a maxim
in order to capture Kant's idea that an action derives its moral worth from being done for the sake of duty itself.
Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C." In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

%:%63=34%:%
%:%64=35%:%
%:%65=36%:%
%:%100=65%:%

@@

%:%114=69%:%
%:%115=70%:%
%:%116=71%:%
%:%125=73%:%
%:%137=75%:%

@@

%:%139=77%:%
%:%141=79%:%
%:%142=79%:%
%:%143=79%:%

@@

%:%148=83%:%

@@

%:%150=85%:%
%:%152=87%:%
%:%153=87%:%
%:%155=88%:%
%:%156=88%:%
%:%158=89%:%
%:%159=90%:%

@@

%:%164=94%:%

@@

%:%166=96%:%
%:%168=98%:%
%:%169=98%:%
%:%170=99%:%
%:%171=100%:%
%:%172=100%:%
%:%173=101%:%
%:%174=102%:%
%:%175=102%:%
%:%176=103%:%
%:%177=104%:%

@@

%:%181=107%:%

@@

%:%183=109%:%
%:%185=111%:%
%:%186=111%:%
%:%187=112%:%
%:%188=113%:%
%:%189=113%:%
%:%190=114%:%

@@

@@

%:%196=122%:%
%:%197=123%:%
%:%198=124%:%
%:%201=126%:%

@@

%:%207=131%:%

@@

%:%209=133%:%
%:%211=135%:%

@@

%:%213=136%:%
%:%214=137%:%
%:%215=138%:%
%:%216=138%:%
%:%218=138%:%
%:%222=138%:%
%:%223=138%:%

@@

%:%226=140%:%
%:%227=141%:%
%:%228=142%:%

@@

%:%245=151%:%

@@

%:%247=153%:%
%:%249=155%:%

@@

%:%251=156%:%
%:%252=157%:%
%:%253=158%:%
%:%254=158%:%
%:%256=158%:%
%:%260=158%:%
%:%261=158%:%

@@

%:%264=160%:%
%:%265=161%:%
%:%266=162%:%

@@

%:%282=171%:%
%:%283=172%:%

@@

%:%286=176%:%

@@

%:%288=177%:%
%:%289=178%:%
%:%290=179%:%
%:%291=179%:%
%:%293=179%:%
%:%297=179%:%
%:%298=179%:%

@@

%:%301=181%:%
%:%302=182%:%
%:%303=183%:%

@@

%:%314=186%:%
%:%315=187%:%
%:%316=188%:%
%:%319=190%:%

@@

%:%324=194%:%

@@

%:%326=196%:%
%:%328=198%:%

@@

%:%330=199%:%
%:%331=200%:%
%:%332=201%:%
%:%333=201%:%
%:%335=201%:%
%:%339=201%:%
%:%340=201%:%

@@

%:%343=203%:%
%:%344=204%:%
%:%345=205%:%
%:%355=207%:%
%:%356=208%:%
%:%365=213%:%

@@

%:%379=217%:%
%:%380=218%:%
%:%381=219%:%
%:%383=220%:%
%:%384=220%:%
%:%385=221%:%
%:%387=222%:%
%:%388=223%:%
%:%389=224%:%
%:%392=226%:%
%:%394=228%:%
%:%395=228%:%
%:%396=229%:%
%:%397=230%:%
%:%398=230%:%
%:%400=230%:%
%:%404=230%:%
%:%405=230%:%

@@

%:%410=234%:%
%:%411=235%:%
%:%412=236%:%
%:%422=238%:%
%:%424=240%:%
%:%425=240%:%
%:%427=242%:%
%:%429=244%:%
%:%430=244%:%
%:%431=244%:%
%:%433=244%:%
%:%437=244%:%
%:%438=244%:%

@@

%:%441=246%:%
%:%442=247%:%
%:%443=248%:%

@@

%:%454=251%:%
%:%455=252%:%
%:%456=253%:%
%:%465=256%:%

@@

%:%483=264%:%
%:%484=265%:%
%:%485=266%:%
%:%489=268%:%
%:%493=270%:%

@@

%:%495=272%:%
%:%497=274%:%
%:%498=274%:%

@@

%:%504=279%:%
%:%505=280%:%
%:%506=281%:%
%:%507=281%:%
%:%508=282%:%
%:%509=283%:%
%:%510=283%:%
%:%511=284%:%
%:%514=285%:%
%:%518=285%:%
%:%519=285%:%
%:%521=286%:%
%:%522=287%:%

@@

%:%547=304%:%
%:%548=305%:%
%:%549=306%:%

@@

%:%554=309%:%
%:%556=311%:%
%:%557=311%:%
%:%559=312%:%
%:%560=312%:%
%:%561=313%:%
%:%562=314%:%
%:%563=314%:%
%:%564=315%:%
%:%567=316%:%
%:%571=316%:%
%:%572=316%:%
%:%573=317%:%
%:%574=317%:%
%:%575=318%:%
%:%576=318%:%
%:%577=319%:%
%:%578=319%:%
%:%579=319%:%
%:%580=320%:%

@@

%:%591=323%:%
%:%592=324%:%
%:%593=325%:%
%:%597=327%:%
%:%601=329%:%
%:%602=330%:%
%:%603=331%:%

@@

%:%608=334%:%
%:%610=336%:%
%:%611=336%:%
%:%624=357%:%
%:%625=358%:%
%:%626=358%:%

@@

%:%631=362%:%
%:%632=363%:%
%:%633=364%:%
%:%634=364%:%
%:%636=365%:%
%:%637=366%:%
%:%638=366%:%
%:%639=367%:%
%:%640=368%:%
%:%641=368%:%
%:%643=369%:%
%:%644=370%:%

@@

%:%648=373%:%
%:%650=375%:%
%:%651=375%:%
%:%652=376%:%
%:%653=377%:%
%:%654=377%:%
%:%656=377%:%
%:%660=377%:%
%:%661=377%:%

@@

%:%667=382%:%
%:%668=383%:%
%:%669=384%:%
%:%679=386%:%
%:%680=387%:%
%:%681=388%:%

@@

%:%687=393%:%
%:%688=394%:%
%:%689=395%:%
%:%692=397%:%
%:%694=399%:%
%:%695=399%:%
%:%696=400%:%
%:%699=401%:%
%:%703=401%:%
%:%704=401%:%
%:%706=402%:%
%:%712=402%:%
%:%715=403%:%
%:%716=404%:%

@@

%:%718=405%:%
%:%719=406%:%
%:%720=407%:%
%:%721=407%:%
%:%723=407%:%
%:%727=407%:%
%:%728=407%:%

@@

%:%732=410%:%
%:%733=411%:%
%:%734=412%:%

@@

%:%750=420%:%
%:%751=421%:%
%:%752=422%:%

@@

%:%765=434%:%
%:%766=435%:%
%:%767=436%:%
%:%776=438%:%
%:%788=440%:%

@@

%:%790=442%:%
%:%792=444%:%

@@

%:%794=445%:%
%:%795=446%:%
%:%796=447%:%
%:%797=447%:%
%:%799=447%:%
%:%803=447%:%
%:%804=447%:%

@@

%:%807=449%:%
%:%808=450%:%
%:%809=451%:%
%:%819=453%:%
%:%820=454%:%
%:%821=455%:%
%:%825=457%:%
%:%827=459%:%

@@

%:%829=460%:%
%:%830=461%:%
%:%831=462%:%
%:%832=462%:%
%:%834=462%:%
%:%838=462%:%
%:%839=462%:%

@@

%:%842=464%:%
%:%843=465%:%
%:%844=466%:%

@@

%:%855=469%:%
%:%857=471%:%

@@

%:%859=472%:%
%:%860=473%:%
%:%861=474%:%
%:%862=474%:%
%:%864=474%:%
%:%868=474%:%
%:%869=474%:%

@@

%:%873=477%:%
%:%874=478%:%
%:%875=479%:%

@@

%:%886=482%:%
%:%888=484%:%
%:%889=484%:%
%:%890=485%:%
%:%891=486%:%
%:%894=487%:%
%:%898=487%:%
%:%899=487%:%
%:%900=487%:%

@@

%:%910=490%:%

@@

%:%912=492%:%
%:%914=494%:%
%:%915=494%:%
%:%916=495%:%
%:%917=496%:%
%:%920=497%:%
%:%924=497%:%
%:%925=497%:%
%:%926=497%:%

@@

%:%936=500%:%
%:%938=502%:%

@@

%:%940=503%:%
%:%941=504%:%
%:%942=505%:%
%:%943=505%:%
%:%945=505%:%
%:%949=505%:%
%:%950=505%:%

@@

%:%953=507%:%
%:%954=508%:%
%:%955=509%:%

@@

%:%968=514%:%

@@

%:%970=516%:%
%:%972=518%:%

@@

%:%975=520%:%
%:%976=521%:%
%:%977=522%:%
%:%978=522%:%
%:%980=522%:%
%:%984=522%:%
%:%985=522%:%

@@

%:%990=526%:%
%:%991=527%:%
%:%992=528%:%

@@

%:%1005=533%:%

@@

%:%1007=535%:%
%:%1009=537%:%
%:%1010=537%:%
%:%1011=538%:%
%:%1012=539%:%
%:%1015=540%:%
%:%1019=540%:%
%:%1020=540%:%
%:%1022=541%:%
%:%1032=543%:%
%:%1033=544%:%
%:%1035=545%:%
%:%1036=545%:%
%:%1037=546%:%
%:%1038=547%:%
%:%1039=547%:%
%:%1041=547%:%
%:%1045=547%:%
%:%1046=547%:%

@@

%:%1050=550%:%
%:%1051=551%:%
%:%1052=552%:%

@@

%:%1076=559%:%
%:%1077=560%:%
%:%1078=561%:%
%:%1087=563%:%

@@

%:%1100=566%:%
%:%1101=567%:%
%:%1102=568%:%

@@

%:%1107=571%:%
%:%1109=573%:%
%:%1110=573%:%
%:%1111=574%:%
%:%1112=575%:%
%:%1113=575%:%
%:%1114=576%:%
%:%1117=577%:%
%:%1121=577%:%
%:%1122=577%:%
%:%1123=577%:%
%:%1125=578%:%
%:%1126=579%:%

@@

%:%1148=593%:%

@@

%:%1150=595%:%
%:%1152=597%:%

@@

%:%1154=598%:%
%:%1155=599%:%
%:%1156=600%:%
%:%1157=600%:%
%:%1159=600%:%
%:%1163=600%:%
%:%1164=600%:%

@@

%:%1169=604%:%
%:%1170=605%:%
%:%1171=606%:%

@@

%:%1182=609%:%
%:%1183=610%:%
%:%1184=611%:%
%:%1188=613%:%

@@

%:%1190=615%:%
%:%1192=617%:%
%:%1193=617%:%
%:%1194=618%:%
%:%1195=618%:%
%:%1197=619%:%
%:%1198=620%:%
%:%1199=620%:%
%:%1200=621%:%
%:%1201=622%:%
%:%1202=622%:%
%:%1203=623%:%
%:%1206=624%:%
%:%1210=624%:%
%:%1211=624%:%
%:%1213=625%:%
%:%1214=626%:%
%:%1215=627%:%

@@

%:%1226=630%:%

@@

%:%1228=632%:%
%:%1230=634%:%
%:%1231=634%:%
%:%1232=635%:%
%:%1234=635%:%
%:%1238=635%:%
%:%1239=635%:%
%:%1241=636%:%
%:%1249=636%:%
%:%1250=637%:%
%:%1251=638%:%
%:%1252=638%:%
%:%1253=639%:%
%:%1255=639%:%
%:%1259=639%:%
%:%1260=639%:%
%:%1262=640%:%
%:%1272=642%:%
%:%1273=643%:%
%:%1274=644%:%
%:%1282=646%:%
